A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-07-03 nips2015.tex
more crisis + fixes: we're ok

Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  The
components of a vector $z \in \mathbb{R}^n$ will be denoted $z_0$,
$z_1$, ..., $z_{n-1}$ (indexing begins from $0$, and not $1$). The
notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
by $\|z\| := \sqrt{z^Tz} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.

@@

\paragraph{\textbf{Convex analysis.}}
Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a convex
  function.
The \textit{effective domain} of $f$, denoted $\dom(f)$ is defined as
\begin{eqnarray}
  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} the function defined by
\begin{eqnarray}
  \prox_f: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
  \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z),
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthongal projectors. One also has the useful
characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

@@

\subsection{Statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1
  \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
\mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1},
e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are
all linear in the size of the game tree (number of states in the game)
and such that Nash equilibria correspond to pairs $(x, y)$ of
\textit{realization plans} which solve the primal LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }e_1^Tp, \hspace{.5em}\text{ subject to }(y,p) \in
     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
    E_1^Tp \geq 0, E_2y = e_2, y \ge 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, A^Tx + E_2^Tq \geq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}.
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0.
  \label{eq:dgap}
\end{equation}

%\subsection{Characterization of equilibria}
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} x^T(-Ay + E_1^Tp) = 0, \hspace{.25em} y^T(A^Tx +
E_2^Tq) = 0.
\label{eq:feasibility}
\end{equation}

@@

In \cite{hoda2010smoothing}, a nested iterative procedure using the
Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to
to solve the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the
following equivalent saddle-point form

\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }x^TAy.
  \label{eq:gilpin}
\end{equation}
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop, though the cost of an iteration is presumably heavy
since it entails computing a $softmax$ at each iteration.

\cite{gilpinfirst} proposed a modified verson of the technqiues in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle (for
example, Nesterov's optimal gradient \cite{nesterov1983}). Here
$\delta = \delta(A, E_1, E_2, e_1, e_2)$ is a certain
\textit{condition number} for the game. It should be noted however that
\begin{itemize}
\item[--] though \cite{gilpinfirst} proved that we always have $\delta
  > 0$, this constant can be arbitrarily small; and most importantly,
\item[--] the reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. Of
  course, the existence of a linear algorithm for solving
  \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  conditions are absent.

@@

In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tp\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

Also define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ by letting
  \begin{equation}
      K :=
      \left[
        \begin{array}{cc}
          A & -E_1^T \\
          E_2 & 0
        \end{array}
        \right],\hspace{.5em}
    \Psi_1(y, p, x, q)
    := \begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}, \hspace{.5em}
      \Psi_2(y, p, x, q) := -\Psi_1(y, p, x, q).
\end{equation}

@@

\begin{proof}
Note that $\dom(g_1) = S_1$ and $\dom(g_2) = S_2$ and observe that the
equilibria of the LCPs \eqref{eq:primal_pb}, \eqref{eq:dual_pb}, and
the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained
in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
q) \in S_1 \times S_2$, the primal-dual gap between the primal
LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
the primal-dual gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
$a(x,y)$, can be computed as
\begin{eqnarray*}
  \begin{aligned}
    a(y,p) &= e_1^Tp +
    i_{\mathbb{R}^{n_2}_+}(y) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) +
    i_{\{0\}}(E_2y - e_2)\\
    &= g_1(y,p) +
    i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
    &= g_1(y,p) + \underset{x' \geq
      0}{\text{max}}\text{ }x'^T(Ay - E_1^Tp) +
    \underset{q'}{\text{max}}\text{ }q'^T(E_2y - e_2)\\
    &= g_1(y,p) + \underset{x',
      q'}{\text{max}}\text{ }x'^TAy - x^TE_1^Tp + q'^TE_2y -
    (i_{\mathbb{R}^{n_1}_+}(x') + e_2^Tq)\\
    &= g_1(y,p)
      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
      q') = g_1(y,p) -\phi_2(y,p),
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between the primal LCP
\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.

@@

\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  $p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow
q^{(k+1)}-q^{(k)}$, \hspace{.5em}$q^{(k+1)}
\leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

>>>>

Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle$ The components of $z \in \mathbb{R}^n$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). The notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
by $\|z\| := \sqrt{\langle z, z\rangle} = \sqrt{\sum_{j=0}^{n - 1}{z_j^2}}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.

@@

\paragraph{\textbf{Convex analysis.}}
Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $\dom(f)$ is defined as
\begin{eqnarray}
  \dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $\dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} the function defined by
\begin{eqnarray}
  \prox_f: \mathbb{R}^n \rightarrow \mathbb{R}^n,\hspace{.5em}x
  \mapsto \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z),
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthongal projectors. One also has the useful
characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

@@

\subsection{Statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1
  \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
\mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1},
e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are
all linear in the size of the game tree (number of states in the game)
and such that Nash equilibria correspond to pairs $(x, y)$ of
\textit{realization plans} which solve the primal LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{ subject to }(y,p) \in
     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
    E_1^Tp \geq 0, E_2y = e_2, y \ge 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, A^Tx + E_2^Tq \geq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}.
\label{eq:polyhedron}
\end{equation}
Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0.
  \label{eq:dgap}
\end{equation}

%\subsection{Characterization of equilibria}
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
\langle y, A^Tx  + E_2^Tq\rangle = 0.
\label{eq:feasibility}
\end{equation}

@@

In \cite{hoda2010smoothing}, a nested iterative procedure using the
Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to
to solve the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} in the
following equivalent saddle-point form\footnote{Note that in
  \cite{hoda2010smoothing}, the roles of $x$ and $y$ are swapped.}

\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle
  \label{eq:gilpin}
\end{equation}
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop, though the cost of an iteration is presumably heavy
since it entails computing a $softmax$ at each iteration.

\cite{gilpinfirst} proposed a modified verson of the technqiues in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle. Here
$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
\textit{condition number} for the game. Their ingenious idea was to
show that \eqref{eq:gilpin} can futher be written in the form\\
\[\mathrm{maximize}\{G(x, y):=G(x, y) :=
max\{\langle x, Av\rangle - \langle u, Ay\rangle |
(u,v) \in Q_1 \times Q_2|(x,y) \in Q_1 \times Q_2\},
\]
and then show that if $\mathcal{E}$ is the set of Nash equilibria for
the game, then  there exists a scalar
$\delta > 0$ such that $distance((x, y), \mathcal{E}) \le \dfrac{G(x, y)}{\delta}$,
for any pair of realization plans $(x, y) \in Q_1 \times Q_2$. Their
algorithm is then to apply Nesterov smoothing with a geometrically
decreasing sequence of tolerance levels on primal-dual gap function $G$.
It should be noted however that
\begin{itemize}
\item[--] Though \cite{gilpinfirst} proved that we always have $\delta
  > 0$, this constant can be arbitrarily small; and most importantly.
\item[--] The reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. For
  example the projections $\proj_{Q_k}$ are applied at each iteration.%%  Of
  %% course, the existence of a linear algorithm for solving
  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  %% conditions are absent.

@@

In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{\mathbb{R}^{n_2}_+}(y) + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{\mathbb{R}^{n_1}_+}(x) + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

Also define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ with $\Psi_2 = -\Psi_1$ by letting
  \begin{equation}
      K :=
      \left[
        \begin{array}{cc}
          A & -E_1^T \\
          E_2 & 0
        \end{array}
        \right],\hspace{.5em}
    \Psi_1(y, p, x, q)
    := \left\langle \begin{bmatrix}x\\q\end{bmatrix},
      K\begin{bmatrix}y\\p\end{bmatrix}\right\rangle.
\end{equation}

@@

\begin{proof}
Note that $\dom(g_1) = S_1$ and $\dom(g_2) = S_2$ and observe that the
equilibria of the LCPs \eqref{eq:primal_pb}, \eqref{eq:dual_pb}, and
the equilibria of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$) are contained
in $S_1 \times S_2$, it suffices to show that at any point $(y, p, x,
q) \in S_1 \times S_2$, the primal-dual gap between the primal
LCP \eqref{eq:primal_pb} and the dual LCP \eqref{eq:dual_pb} equals
the primal-dual gap of GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
$a(x,y)$, can be computed as
\begin{eqnarray*}
  \begin{aligned}
    a(y,p) &= \langle e_1,p\rangle + i_{y\ge 0} + i_{-Ay + E_1^Tp \ge 0} +
    i_{E_2y = e_2}\\
    &= g_1(y,p) + \underset{x' \geq
      0}{\text{max}}\text{ }\langle x',Ay - E_1^Tp\rangle +
    \underset{q'}{\text{max}}\text{ }\langle q',E_2y - e_2\rangle\\
    &= g_1(y,p) + \underset{x',
      q'}{\text{max}}\text{ }\langle x',Ay\rangle - \langle x',
    E_1^Tp\rangle + \langle q',E_2y\rangle -
    (i_{x' \ge 0} + \langle e_2,q\rangle)\\
    &= g_1(y,p)
      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
      q') = g_1(y,p) -\phi_2(y,p),
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}

where $-\infty \le \phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') < +\infty$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
-\langle q, e_2\rangle -i_{x \ge 0} - i_{A^Tx+E_2^Tq \ge 0} -
 i_{E_1x = e_1}\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }\langle y', A^Tx + E_2^Tq\rangle +
 \underset{p'}{\text{min}}\text{ }\langle p', e_1-E_1x\rangle\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $-\infty \le \phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) < +\infty$.
Thus, one can compute the primal-dual gap between the primal LCP
\eqref{eq:primal_pb} and dual the LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.

@@

\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \epsilon$ or
  $\|{v}_{a}^{(k)}\|/k \ge \rho$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}
